babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-03-06 article.tex
Spellcheck
Feedback, thanks @rsetienne

However, for exploring the output of many BEAST2 runs, 
one would like a script to collect all parameters' ESSes,
parameter traces and posterior phylogenies.
There is no single package that offers a complete solution,
but examples of R packages that offer a partial solution
are \verb;BEASTmasteR;, \verb;rBEAST; 
(\cite{rBEAST_ratmann}) and 
\verb;RBeast; (\cite{RBeast_faria}). 
\verb;BEASTmasteR; is a partial BEAUti alternative,
does not offer a way to call BEAST2, 
nor allows for the same data analysis as done by Tracer. 
\verb;RBeast; provides some plotting options and parsing
of BEAST2 output files. \verb;rBEAST; is a package developed
around testing a biological hypothesis, 
that does not aim to be a generally used package.

@@

\verb;babette; is free, libre and open source software available 
from the official R package archive at 
\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#babette}
and is licensed under the GNU General Public License v3.0.
\verb;babette; uses the Travis CI (\url{https://travis-ci.org})
continuous integration service, which is known to significantly 
increase the number of bugs exposed (\cite{vasilescu2015}) and increases
the speed at which new features are added (\cite{vasilescu2015}).
\verb;babette; has a 100\% code coverage, which correlates with 
code quality (\cite{horgan1994,del1995correlation}). 
\verb;babette; follows Hadley Wickham's style guide (\cite{style_guide}), 
which improves software quality (\cite{fang2001}).
\verb;babette; dependends on multiple packages, which are 
\verb;ape; (\cite{APE}), 
\verb;beautier; (\cite{beautier}),
\verb;beastier; (\cite{beastier}),
\verb;devtools; (\cite{devtools}),
\verb;geiger; (\cite{GEIGER}),
\verb;ggplot2; (\cite{ggplot2}),
\verb;knitr; (\cite{knitr}),
\verb;phangorn; (\cite{phangorn}),
\verb;rmarkdown; (\cite{rmarkdown}),
\verb;seqinr; (\cite{seqinr}),
\verb;stringr; (\cite{stringr}),
\verb;testit; (\cite{testit}) and 
\verb;tracerer; (\cite{tracerer}).
\verb;babette; is tested to give a clean 
error message for incorrect input, by
calling \verb;babette; one million times
with random or random sensible inputs, 
using the Peregrine high performance computer cluster. 
The scripts to do so, are supplied with \verb;babette;.

>>>>

However, for exploring the output of many BEAST2 runs, one would like a
script to collect all parameters' ESSes, parameter traces and posterior
phylogenies. There is no single package that offers a complete solution,
but examples of R packages that offer a partial solution are rBEAST
(\cite{rBEAST_ratmann}) and RBeast (\cite{RBeast_faria}). RBeast provides some
plotting options and parsing of BEAST2 output files, but the plotting
functions are too specific for general use, where the functions for parsing
call those of \verb;babette;. rBEAST was developed to test a 
particular biological hypothesis (\cite{ratmann2016}), 
and hence was not designed for general use.

@@

\verb;babette; is free, libre and open source software available 
from the official R package archive at 
\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#babette}
and is licensed under the GNU General Public License v3.0.
\verb;babette; uses the Travis CI (\url{https://travis-ci.org})
continuous integration service, which is known to significantly 
increase the number of bugs exposed (\cite{vasilescu2015}) and increases
the speed at which new features are added (\cite{vasilescu2015}).
\verb;babette; has a 100\% code coverage, which correlates with 
code quality (\cite{horgan1994,del1995correlation}). 
\verb;babette; follows Hadley Wickham's style guide (\cite{style_guide}), 
which improves software quality (\cite{fang2001}).
\verb;babette; depends on multiple packages, which are 
\verb;ape; (\cite{APE}), 
\verb;beautier; (\cite{beautier}),
\verb;beastier; (\cite{beastier}),
\verb;devtools; (\cite{devtools}),
\verb;geiger; (\cite{GEIGER}),
\verb;ggplot2; (\cite{ggplot2}),
\verb;knitr; (\cite{knitr}),
\verb;phangorn; (\cite{phangorn}),
\verb;rmarkdown; (\cite{rmarkdown}),
\verb;seqinr; (\cite{seqinr}),
\verb;stringr; (\cite{stringr}),
\verb;testit; (\cite{testit}) and 
\verb;tracerer; (\cite{tracerer}).
\verb;babette; is tested to give a clean 
error message for incorrect input, by
calling \verb;babette; one million times
with random or random sensible inputs, 
using the Peregrine high performance computer cluster. 
The scripts to do so, are supplied with \verb;babette;.
